---
title: "Section Education: Formal Education"
author: "Hemen Boro"
date: "6/15/2019"
output:
html_document: default
theme: cerulean  
---

Setting the working directory
```{r setup, include=FALSE, echo=FALSE}
require("knitr")
opts_knit$set(root.dir = 'D://personal/swb project/files_bts')

```

Initialize library
```{r echo=FALSE, message=FALSE, r,warning=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(xlsx)
library(tidyverse)
library(plyr)
library(reshape2)
library(wordcloud)
library(tidytext)##
library(ggpubr)## ballomnplot
library(readxl)##reading excel
library(stringi)#string operations
library(tm)##wordcloud
library(SnowballC)##wordcloud
library(wordcloud)##wordcloud
library(RColorBrewer)##wordcloud
library(ggcorrplot)##correlogram plot
library(qdapRegex) ##removing emotions
library(knitr)
```
Loding files
```{r,warning=FALSE,message=FALSE}

### pre questionnaire BTS 2017-18

PreQ.PrevYear <- read_excel("Copy of Student Pre-Questionnaire Back-to-School 2017-2018 Group (Afghanistan).xlsx")


```










Removing all the smiley
```{r}
PreQ.PrevYear <- tail(PreQ.PrevYear,-1)
# Removing emoticons because one set of questionnaire responses have them and the other don't
PreQ.PrevYear[] <- lapply(PreQ.PrevYear, gsub, pattern=':)', replacement='')
PreQ.PrevYear[] <- lapply(PreQ.PrevYear, gsub, pattern=':D', replacement='')
PreQ.PrevYear[] <- lapply(PreQ.PrevYear, gsub, pattern=':|', replacement='')
PreQ.PrevYear[] <- lapply(PreQ.PrevYear, gsub, pattern=':/', replacement='')
PreQ.PrevYear[] <- lapply(PreQ.PrevYear, gsub, pattern='_', replacement='')
PreQ.PrevYear[] <- lapply(PreQ.PrevYear, gsub, pattern='|', replacement='')
PreQ.PrevYear[] <- lapply(PreQ.PrevYear, gsub, pattern='/', replacement='')

```
Renaming all the columns and transforming

```{r}
colnames(PreQ.PrevYear)[colnames(PreQ.PrevYear)=="Project Site:"] <- "Project.Site"

```
```{r}
PreQ.PrevYear <- PreQ.PrevYear %>%
  replace(is.na(.), "") %>%
  dplyr::rename("Project_Site" ="Project.Site") %>%
  dplyr::rename("Gender" = "What is your gender?") %>%
  dplyr::rename("My experience coming to BTS classes has been" = "My experience coming to BTS classes has been... [R5]") %>%
  dplyr::rename("Why (experience coming to BTS classes)" = "...13") %>%
  dplyr::rename("Why (feeling safe at Skateistan)" = "...15") %>%
  dplyr::rename("Confidence since joining the program has" = "Having confidence means that you feel good about yourself and you believe you can take on new challenges, big or small, that you may face in life. Since joining the program my confidence has... [R2]") %>%
  dplyr::rename("Comment on confidence levels" = "...17") %>%
  dplyr::rename("I have learned a lot of useful skills and lessons since coming to BTS classes at Skateistan" = "I have learned a lot of useful skills and lessons since coming to BTS classes at Skateistan.") %>%
  dplyr::rename("Comment on useful skills learnt" = "...19") %>%
  dplyr::rename("Friends made at Skateistan" = "Since coming to Skateistan I have made a new friend from a different background (ethnicity, disability, family income)") %>%
  dplyr::rename("How many friends made/background" = "...21") %>%
  dplyr::rename("Role Model - Mother" = "When I have problems or I am upset, I can talk to: (you can choose more than one answer)") %>%
  dplyr::rename("Role Model - Father" = "...23") %>%
  dplyr::rename("Role Model - Brother/Sister" = "...24") %>%
  dplyr::rename("Role Model - Other family member" = "...25") %>%
  dplyr::rename("Role Model - Friends at Skateistan" = "...26") %>%
  dplyr::rename("Role Model - Skateistan Educator" = "...27") %>%
  dplyr::rename("Role Model - Someone older than me at Skateistan" = "...28") %>%
  dplyr::rename("Role Model - Other" = "...29") %>%
  dplyr::rename("Role Model - Would you like to say who?" = "...30") %>%
  dplyr::rename("Comment on reading and writing" = "...32") %>%
  dplyr::rename("Comment on good at math" = "...34") %>%
  dplyr::rename("Comment on good at skateboarding/sports" = "...36") %>%
  tidyr::unite("Tell us about your work history", "Tell us about your work history", "...38","...39", "...40", sep = "", remove = TRUE) %>%
  dplyr::rename("Would you like to say what kind of work? If you have stopped working, please explain why" = "...41") %>%
  dplyr::rename("My parents/family want me to complete my education until" = "My parents/family want me to complete my education until...") %>%
  dplyr::rename("Education level - Why/why not?" = "...43")
PreQ.PrevYear$`Friends made at Skateistan`[PreQ.PrevYear$`Friends made at Skateistan` == "Yes, more than one new friend from a different background"] <- "Yes, more than one new friend"
PreQ.PrevYear$`Friends made at Skateistan`[PreQ.PrevYear$`Friends made at Skateistan` == "Yes, one new friend from a different background"] <- "Yes, one new friend"
PreQ.PrevYear$`I am good at reading and writing`[PreQ.PrevYear$`I am good at reading and writing` == "Neural"] <- "Neutral"
PreQ.PrevYear$`I am good at reading and writing`[PreQ.PrevYear$`I am good at reading and writing` == "Strongly agree"] <- "Strongly Agree"

```
After transformation columnsa and uniting
```{r}
head(PreQ.PrevYear)

```
Visulization
##### gender studies####################
```{r}


# cross tab for frequency counts for location and gender

Freq_table_gender_location<- table(PreQ.PrevYear$Project_Site,PreQ.PrevYear$Gender)
Freq_table_gender_location_df<- as.data.frame(Freq_table_gender_location)
Freq_table_gender_location_df<- Freq_table_gender_location_df[c(-1,-2),]### freq table for gender based on location 
names(Freq_table_gender_location_df)[1:2]<-paste(c("Project_Sites","Gender"))  ### renaming the column names
#Freq_table_gender_location_df<- Freq_table_gender_location_df[c(-1,-2),]  ### freq table for gender based on location
Freq_table_gender_location_df
```



```{r,fig.width=14, fig.height=12}
### creating an barplot ---- freq count of gender in project_sites 

gender_count_barplot<-ggplot(data=Freq_table_gender_location_df, aes(x=Project_Sites, y=Freq, fill=Gender)) +geom_bar(stat="identity", position=position_dodge())
gender_count_barplot<-gender_count_barplot+geom_text(aes(label=Freq), vjust=1.6, color="white",position = position_dodge(0.9), size=10)+scale_fill_brewer(palette="Paired")+theme_minimal()                
gender_count_barplot


```
#### role model studies
```{r}
#extracting all role model columns with gender and project sites
Freq_table_role_model<- PreQ.PrevYear %>% 
  dplyr:: select("Project_Site","Gender","Role Model - Father","Role Model - Brother/Sister","Role Model - Other family member","Role Model - Friends at Skateistan","Role Model - Skateistan Educator","Role Model - Someone older than me at Skateistan","Role Model - Other","Role Model - Would you like to say who?")
Freq_table_role_model[Freq_table_role_model==""]<- "Not Available"  # removing blanks with NA values

```

```{r}
#### transforming role model column and calculating frequency count####

role_model_freq_counts<- lapply(Freq_table_role_model,table)

### converting to dataframe and reshape the structure of dataframe
role_model_freq_counts_reshape<-as.data.frame(melt(role_model_freq_counts)) #### reshaping the list to an required table
col_role_model<- c("L1","Var1","value")## column na,es of reshape dataframe
role_model_freq_counts_reshape<- role_model_freq_counts_reshape[,col_role_model] ## arranging column for role model dataframe
role_model_freq_counts_reshape

## spreading the structure of dataframe
role_model_freq_counts_reshape_table<-role_model_freq_counts_reshape%>%spread(Var1,value)

```
```{r,fig.width=14, fig.height=12}
### Balloon plot of role model

rolemodel_freqcount_balloonplot<- ggballoonplot(role_model_freq_counts_reshape, fill = "value")+
  scale_fill_viridis_c(option = "C")
rolemodel_freqcount_balloonplot

```
```{r,fig.width=14, fig.height=12}
### heatmap
role_model_freq_counts_reshape_heatmap<-role_model_freq_counts_reshape%>%spread(L1,value)
role_model_freq_counts_reshape_heatmap<- as.data.frame(role_model_freq_counts_reshape_heatmap)
role_model_freq_counts_reshape_heatmap[is.na(role_model_freq_counts_reshape_heatmap)] <- 0
role_model_freq_counts_reshape_heatmap2 <- as.matrix(role_model_freq_counts_reshape_heatmap[, -1])
rownames(role_model_freq_counts_reshape_heatmap2) <- role_model_freq_counts_reshape_heatmap$Var1
heatmap(role_model_freq_counts_reshape_heatmap2)

```
```{r,fig.width=14, fig.height=12}

### corelogram

role_model_correltion<-role_model_freq_counts_reshape_heatmap[,-1]
#rownames(role_model_correltion)<-colnames(role_model_correltion)
M<-round(cor(role_model_correltion),1)
ggcorrplot(M,hc.order = TRUE,type='lower',lab=TRUE,lab_size=3, method="circle",colors = c("tomato2", "white", "springgreen3"), ggtheme=theme_bw,title="Correlogram of role models")


```
```{r,fig.width=14, fig.height=12}
#### sentimental analysis #####

#extracting all the Role Model - Would you like to say who? rows 

role_model_who_says<- role_model_freq_counts_reshape %>% 
  filter(L1=="Role Model - Would you like to say who?")

## transforming text from role model

role_model_who_says<-role_model_who_says[2]
role_vec <- as.matrix(role_model_who_says)
role_vec_spl_cha_remove<- gsub(".","",role_vec,fixed=TRUE)
role_vec_spl_cha_remove<- as.vector(role_vec_spl_cha_remove)





## extract role ansers  columns

##corpus

docs<- Corpus(VectorSource(role_vec_spl_cha_remove))

# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("blabla1", "blabla2")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
# docs <- tm_map(docs, stemDocument)



dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
rownames(d)<- NULL ## remove rownames from dataframe
d<-d %>% filter(word !="null")

p<-ggplot(d,aes(word,freq))+geom_bar(stat="identity")+geom_text(aes(label=freq))
p<-p+theme(axis.text.x = element_text(angle = 90, hjust = 1))

word_rolemodel<-wordcloud(words = d$word, freq = d$freq, min.freq = 1,max.words=100, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))
word_rolemodel


```
```{r}
### pre questionnaire BTS 2018-19
PreQ.CurrYear <- read_excel("Copy of Student Pre-Questionnaire Back-to-School 2018-2019 Group (Afghanistan).xlsx")

colnames(PreQ.CurrYear)[colnames(PreQ.CurrYear)=="Project Site"] <- "Project_Site"
head(PreQ.CurrYear)
```
Cleaning the dataset


```{r}
PreQ.CurrYear <- tail(PreQ.CurrYear,-1)
require(dplyr)
PreQ.CurrYear <- PreQ.CurrYear %>%
  #as.Date(as.character(as.POSIXct("Start Date"),format="%Y-%m-%d")) %>%
  #as.Date(as.character(as.POSIXct("End Date"),format="%Y-%m-%d")) %>%
  replace(is.na(.), "") %>%
  tidyr::unite("Project.Site", "Project_Site","...11", sep = "", remove = TRUE) %>%
  tidyr::unite("Gender", "What is your gender?", "...14","...15", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can work well in a team/group", "I believe I can......16", "...17","...18", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can speak in front of the class (public speaking)", "...19", "...20","...21", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can help other people", "...22", "...23","...24", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can ask for help when I have a problem", "...25", "...26","...27", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can make mistakes and learn from them", "...28", "...29","...30", sep = "", remove = TRUE) %>%
  dplyr::rename("Examples (I believe section)" = "...31") %>%
  tidyr::unite("How do you feel traveling to/from Skateistan", "How do you feel...", "...33","...34", sep = "", remove = TRUE) %>%
  tidyr::unite("How do you feel in the skatepark", "...35", "...36","...37", sep = "", remove = TRUE) %>%
  tidyr::unite("How do you feel in the classroom", "...38", "...39","...40", sep = "", remove = TRUE) %>%
  tidyr::unite("How do you feel talking with an Educator at Skateistan", "...41", "...42","...43", sep = "", remove = TRUE) %>%
  tidyr::unite("How do you feel learning with my class volunteer / youth leader", "...44", "...45","...46", sep = "", remove = TRUE) %>%
  dplyr::rename("Examples (How do you feel section)" = "...47") %>%
  tidyr::unite("In general I like myself", "In general I…", "...49","...50", sep = "", remove = TRUE) %>%
  dplyr::rename("What makes you feel good/confident? What do you like about yourself?" = "...51") %>%
  tidyr::unite("I believe I can spend time studying", "I believe I can......52", "...53","...54", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can do well in school", "...55", "...56","...57", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can enjoy sport/skateboarding skills", "...58", "...59","...60", sep = "", remove = TRUE) %>%
  tidyr::unite("I believe I can learn new skateboard tricks", "...61", "...62","...63", sep = "", remove = TRUE) %>%
  dplyr::rename("Examples (I believe I can section)" = "...64") %>%
  tidyr::unite("I am good at reading", "I am good at....", "...66","...67", sep = "", remove = TRUE) %>%
  tidyr::unite("I am good at writing", "...68", "...69","...70", sep = "", remove = TRUE) %>%
  tidyr::unite("I am good at math", "...71", "...72","...73", sep = "", remove = TRUE) %>%
  tidyr::unite("I am good at skateboarding", "...74", "...75","...76", sep = "", remove = TRUE) %>%
  tidyr::unite("I am good at other sports", "...77", "...78","...79", sep = "", remove = TRUE) %>%
  dplyr::rename("Examples (I am good at section)" = "...80") %>%
  tidyr::unite("Over the past 2-3 weeks I have felt happy", "Over the past 2-3 weeks...", "...82","...83", sep = "", remove = TRUE) %>%
  tidyr::unite("Over the past 2-3 weeks I have felt calm and relaxed", "...84", "...85","...86", sep = "", remove = TRUE) %>%
  tidyr::unite("Over the past 2-3 weeks I wake up feeling fresh and rested", "...87", "...88","...89", sep = "", remove = TRUE) %>%
  tidyr::unite("Over the past 2-3 weeks My daily life has been filled with things that interest me", "...90", "...91","...92", sep = "", remove = TRUE) %>%
  dplyr::rename("Role Model - Mother" = "When I have problems or I am upset, I can talk to... (you can choose more than one) (Role Model)") %>%
  dplyr::rename("Role Model - Father" = "...94") %>%
  dplyr::rename("Role Model - Brother" = "...95") %>%
  dplyr::rename("Role Model - Sister" = "...96") %>%
  dplyr::rename("Role Model - Other family member" = "...97") %>%
  dplyr::rename("Role Model - Friends at Skateistan" = "...98") %>%
  dplyr::rename("Role Model - Skateistan Educator" = "...99") %>%
  dplyr::rename("Role Model - Someone older than me at Skateistan" = "...100") %>%
  dplyr::rename("Role Model - Other" = "...101") %>%
  dplyr::rename("Role Model - Not sure" = "...102") %>%
  dplyr::rename("Role Model - Would you like to say who? How do you feel when you talk to them about your problems?" = "...103") %>%
  tidyr::unite("My parents/family want me to complete my education until", "My parents/family want me to complete my education until...", "...105","...106", "...107", "...108", sep = "", remove = TRUE) %>%
  dplyr::rename("Education level - Why/why not?" = "...109")

### removing smiley
PreQ.CurrYear[] <- lapply(PreQ.CurrYear, rm_emoticon)

### removing smiley

PreQ.CurrYear[] <- lapply(PreQ.CurrYear, rm_emoticon)

###after transformation
head(PreQ.CurrYear)
```
#### Visulization ######

```{r}


### 1. gender studies

# cross tab for frequency counts for location and gender

PreQ.CurrYear_gender_location_count<- table(PreQ.CurrYear$Project.Site,PreQ.CurrYear$Gender)
PreQ.CurrYear_gender_location_count<- PreQ.CurrYear_gender_location_count[c(-1),]
PreQ.CurrYear_gender_location_count<- as.data.frame(PreQ.CurrYear_gender_location_count)
names(PreQ.CurrYear_gender_location_count)[1:2]<-paste(c("Project_Sites","Gender"))
PreQ.CurrYear_gender_location_count

```

```{r,fig.width=14, fig.height=12}
### creating an barplot ---- freq count of gender in project_sites 

gender_count_barplot<-ggplot(data=PreQ.CurrYear_gender_location_count, aes(x=Project_Sites, y=Freq, fill=Gender)) +geom_bar(stat="identity", position=position_dodge())
gender_count_barplot<-gender_count_barplot+geom_text(aes(label=Freq), vjust=1.6, color="white",position = position_dodge(0.9), size=10)+scale_fill_brewer(palette="Paired")+theme_minimal()                
gender_count_barplot

```
```{r}
#### role model studies

#extracting all role model columns with gender and project sites
role_model_preq_currentyr<- PreQ.CurrYear %>% select(matches('Proj|Gende|Role'))
                                                
role_model_preq_currentyr[role_model_preq_currentyr==""]<- "Not Available"  # removing blanks with NA values
role_model_preq_currentyr

```

```{r}
#### transforming role model column and calculating frequency count####

role_model_preq_currentyr_counts<- lapply(role_model_preq_currentyr,table)
role_model_preq_currentyr_counts

### converting to dataframe and reshape the structure of dataframe
role_model_freq_counts_reshape_currentyr<-as.data.frame(melt(role_model_preq_currentyr_counts)) #### reshaping the list to an required table

names(role_model_freq_counts_reshape_currentyr)[1:3]<-paste(c("Responses","Value","Questions"))


col_role_models<- c("Questions","Responses","Value")## column na,es of reshape dataframe
role_model_freq_counts_reshape_currentyr<-role_model_freq_counts_reshape_currentyr[,col_role_models] ## arranging column for role model dataframe

role_model_freq_counts_reshape_currentyr
```
```{r}
## spreading the structure of dataframe
role_model_freq_counts_reshape_currentyr_table<-role_model_freq_counts_reshape_currentyr%>%spread(Responses,Value)
role_model_freq_counts_reshape_currentyr_table
```
```{r,fig.width=14, fig.height=12}
### Balloon plot of role model

rolemodel_freqcount_balloonplot_curryr<- ggballoonplot(role_model_freq_counts_reshape_currentyr, fill = "value")+
  scale_fill_viridis_c(option = "C")
rolemodel_freqcount_balloonplot_curryr



```

### Heatmap
```{r,fig.width=14, fig.height=12}
role_model_freq_counts_reshape_heatmap_cy<-role_model_freq_counts_reshape_currentyr%>%spread(Questions,Value)

role_model_freq_counts_reshape_heatmap_cy<- as.data.frame(role_model_freq_counts_reshape_heatmap_cy)
role_model_freq_counts_reshape_heatmap_cy[is.na(role_model_freq_counts_reshape_heatmap_cy)] <- 0
role_model_freq_counts_reshape_heatmap2_cy <- as.matrix(role_model_freq_counts_reshape_heatmap_cy[, -1])
rownames(role_model_freq_counts_reshape_heatmap2_cy) <- role_model_freq_counts_reshape_heatmap_cy$Responses
heatmap(role_model_freq_counts_reshape_heatmap2_cy)
```
##correlation plot

```{r,fig.width=14, fig.height=12}
role_model_correltion_cy<-role_model_freq_counts_reshape_heatmap2_cy[,-1]
#rownames(role_model_correltion_cy)<-colnames(role_model_correltion_cy)
M<-round(cor(role_model_correltion_cy),1)
ggcorrplot(M,hc.order = TRUE,type='lower',lab=TRUE,lab_size=3, method="circle",colors = c("tomato2", "white", "springgreen3"), ggtheme=theme_bw,title="Correlogram of role models")


```
#### sentimental analysis #####

#extracting all the Role Model - Would you like to say who? rows 
```{r}
Role_Model_who_says_curryr<- role_model_freq_counts_reshape_currentyr %>% 
  filter(Questions=="Role Model - Would you like to say who? How do you feel when you talk to them about your problems?")

Role_Model_who_says_curryr

```
```{r}
## transforming text from role model

Role_Model_who_says_curryr<-Role_Model_who_says_curryr[2]
role_vec_cy <- as.matrix(Role_Model_who_says_curryr)
role_vec_spl_cha_remove_cy<- gsub(".","",role_vec_cy,fixed=TRUE)
role_vec_spl_cha_remove_cy<- as.vector(role_vec_spl_cha_remove_cy)
role_vec_spl_cha_remove_cy
```

```{r,fig.width=14, fig.height=12}
## extract role answers  columns

##corpus

docs_cy<- Corpus(VectorSource(role_vec_spl_cha_remove_cy))

# Convert the text to lower case
docs_cy <- tm_map(docs_cy, content_transformer(tolower))
# Remove numbers
docs_cy <- tm_map(docs_cy, removeNumbers)
# Remove english common stopwords
docs_cy <- tm_map(docs_cy, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
# Remove punctuations
docs_cy <- tm_map(docs_cy, removePunctuation)
# Eliminate extra white spaces
docs_cy <- tm_map(docs_cy, stripWhitespace)
# Text stemming
docs_cy <- tm_map(docs_cy, stemDocument)



dtm_cy <- TermDocumentMatrix(docs_cy)
m_cy <- as.matrix(dtm_cy)
v_cy <- sort(rowSums(m_cy),decreasing=TRUE)
d_cy <- data.frame(word = names(v_cy),freq=v_cy)
rownames(d_cy)<- NULL ## remove rownames from dataframe
d_cy<-d_cy %>% filter(word !="null")

p_cy<-ggplot(d_cy,aes(word,freq))+geom_bar(stat="identity")+geom_text(aes(label=freq))
p_cy<-p+theme(axis.text.x = element_text(angle = 90, hjust = 1))

word_rolemodel_cy<-wordcloud(words = d_cy$word,freq = d_cy$freq, min.freq = 1,max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))
word_rolemodel_cy

```
```{r}
### post questionnaire BTS 2017-18
PostQ.PrevYear <- read_excel("Copy of Student Post-Questionnaire Back-to-School 2017-2018 Graduating Group (Afghanistan).xlsx")
PostQ.PrevYear


```
```{r}
PostQ.PrevYear <- tail(PostQ.PrevYear,-1)
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern=' :)', replacement='')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern=' :D', replacement='')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern=':|', replacement='')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern=':/', replacement='')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern='_', replacement='')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern='|', replacement='')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern='/', replacement='')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern='Neural', replacement='Neutral')
PostQ.PrevYear[] <- lapply(PostQ.PrevYear, gsub, pattern='agree', replacement='Agree')
head(PostQ.PrevYear)


```
```{r}
PostQ.PrevYear <- PostQ.PrevYear %>%
  replace(is.na(.), "") %>%
  tidyr::unite("Project Site", "Project Site:", "...11", sep = "", remove = TRUE) %>%
  tidyr::unite("Group Name", "What is your Group name?", "...13", "...14", "...15", "...16", sep = "", remove = TRUE) %>%
  dplyr::rename("Name" = "What is your name? (Optional)") %>%
  tidyr::unite("Gender", "What is your gender?", "...19", "...20", sep = "", remove = TRUE) %>%
  tidyr::unite("My experience coming to BTS classes has been", "My experience coming to BTS classes has been... [R5]",
               "...22", "...23", "...24", "...25", sep = "", remove = TRUE) %>%
  dplyr::rename("Comment (experience coming to BTS classes)" = "...26") %>%
  tidyr::unite("How safe do you feel at Skateistan?", "How safe do you feel at Skateistan?", "...28", "...29", "...30", "...31", sep = "", remove = TRUE) %>%
  dplyr::rename("Comment (safety at Skateistan)" = "...32") %>%
  tidyr::unite("Confidence since joining the program has", "Having confidence means that you feel good about yourself and you believe you can take on new challenges, big or small, that you may face in life. Since joining the program my confidence has... [R2]",
               "...34", "...35", "...36", "...37", sep = "", remove = TRUE) %>%
  dplyr::rename("Comment (confidence since joining Skateistan)" = "...38") %>%
  tidyr::unite("I have learned a lot of useful skills and lessons since coming to BTS classes at Skateistan",
               "I have learned a lot of useful skills and lessons since coming to BTS classes at Skateistan.", "...40", "...41", "...42",
               "...43", sep = "", remove = TRUE) %>%
  dplyr::rename("Comment (what you have learnt)" = "...44") %>%
  tidyr::unite("Friends made at Skateistan","Since coming to Skateistan I have made a new friend ", "...46", "...47", "...48", sep = "", remove = TRUE) %>%
  dplyr::rename("Comment (on friends made)" = "...49") %>%
  dplyr::rename("Role Model - Mother" = "When I have problems or I am upset, I can talk to: (you can choose more than one answer)") %>%
  dplyr::rename("Role Model - Father" = "...51") %>%
  dplyr::rename("Role Model - Brother/Sister" = "...52") %>%
  dplyr::rename("Role Model - Other family member" = "...53") %>%
  dplyr::rename("Role Model - Friends at Skateistan" = "...54") %>%
  dplyr::rename("Role Model - Skateistan Educator" = "...55") %>%
  dplyr::rename("Role Model - Someone older than me at Skateistan" = "...56") %>%
  dplyr::rename("Role Model - Other" = "...57") %>%
  dplyr::rename("Role Model - Would you like to say who?" = "...58") %>%
  tidyr::unite("I am good at reading and writing", "I am good at...", "...60", "...61", "...62", "...63", sep = "", remove = TRUE) %>%
  tidyr::unite("I am good at math", "...64", "...65", "...66", "...67", "...68", sep = "", remove = TRUE) %>%
  tidyr::unite("I am good at skateboarding and sports", "...69", "...70", "...71", "...72", "...73", sep = "", remove = TRUE) %>%
  tidyr::unite("I am good at other sports", "...74", "...75", "...76", "...77", "...78", sep = "", remove = TRUE) %>%
  dplyr::rename("Comment on other sports" = "...79") %>%
  tidyr::unite("Tell us about your work history", "Tell us about your work history", "...81","...82", "...83", sep = "", remove = TRUE) %>%
  dplyr::rename("Would you like to say what kind of work? If you have stopped working, please explain why" = "...84") %>%
  tidyr::unite("My parents/family want me to complete my education until", "My parents/family want me to complete my education until...",
               "...86", "...87", "...88", "...89", sep = "", remove = TRUE) %>%
  dplyr::rename("Education level - Why/why not?" = "...90") 
PostQ.PrevYear$`I am good at math`[PostQ.PrevYear$`I am good at math` == "Neutral |"] <- "Neutral"
PostQ.PrevYear$`I am good at reading and writing`[PostQ.PrevYear$`I am good at reading and writing` == "Neutral |"] <- "Neutral"
PostQ.PrevYear$`I have learned a lot of useful skills and lessons since coming to BTS classes at Skateistan`[PostQ.PrevYear$`I have learned a lot of useful skills and lessons since coming to BTS classes at Skateistan` == "Neutral |"] <- "Neutral"
PostQ.PrevYear


```
```{r}




### 1. gender studies

# cross tab for frequency counts for location and gender

Post.prevYear_gender_location_count<- table(PostQ.PrevYear$`Project Site`,PostQ.PrevYear$Gender)
Post.prevYear_gender_location_count
#Post.prevYear_gender_location_count<- Post.prevYear_gender_location_count[c(-1),]
#Post.prevYear_gender_location_count
Post.prevYear_gender_location_count<- as.data.frame(Post.prevYear_gender_location_count)
Post.prevYear_gender_location_count
names(Post.prevYear_gender_location_count)[1:2]<-paste(c("Project_Sites","Gender"))
Post.prevYear_gender_location_count

```

```{r}

post_prevyear_gender_count_barplot<-ggplot(data=Post.prevYear_gender_location_count, aes(x=Project_Sites, y=Freq, fill=Gender)) +geom_bar(stat="identity", position=position_dodge())
post_prevyear_gender_count_barplot<-post_prevyear_gender_count_barplot+geom_text(aes(label=Freq), vjust=1.6, color="white",position = position_dodge(0.9), size=10)+scale_fill_brewer(palette="Paired")+theme_minimal()                
post_prevyear_gender_count_barplot



```
```{r}


#extracting all role model columns with gender and project sites
role_model_post_prevyr<- PostQ.PrevYear%>% select(matches('Proj|Gende|Role'))
role_model_post_prevyr[role_model_post_prevyr==""]<- "Not Available"  # removing blanks with NA values
role_model_post_prevyr

```
```{r}
#### transforming role model column and calculating frequency count####

role_model_post_prevyr_counts<- lapply(role_model_post_prevyr,table)
role_model_post_prevyr_counts

### converting to dataframe and reshape the structure of dataframe
role_model_freq_counts_reshape_post_prevyr<-as.data.frame(melt(role_model_post_prevyr_counts)) #### reshaping the list to an required table

names(role_model_freq_counts_reshape_post_prevyr)[1:3]<-paste(c("Responses","Value","Questions"))


col_role_models<- c("Questions","Responses","Value")## column na,es of reshape dataframe
role_model_freq_counts_reshape_post_prevyr<-role_model_freq_counts_reshape_post_prevyr[,col_role_models] ## arranging column for role model dataframe

role_model_freq_counts_reshape_post_prevyr



```
```{r}

role_model_freq_counts_reshape_post_prevyr_table<-role_model_freq_counts_reshape_post_prevyr%>%spread(Responses,Value)
role_model_freq_counts_reshape_post_prevyr_table

```
```{r,fig.width=14, fig.height=12}
### Balloon plot of role model

rolemodel_freqcount_balloonplot_post_prevyr<- ggballoonplot(role_model_freq_counts_reshape_post_prevyr, fill = "value")+
  scale_fill_viridis_c(option = "C")
rolemodel_freqcount_balloonplot_post_prevyr



```
#Heatmap
```{r,fig.width=14, fig.height=12}
role_model_freq_counts_reshape_heatmap_post_prevyr<-role_model_freq_counts_reshape_post_prevyr%>%spread(Questions,Value)


role_model_freq_counts_reshape_heatmap_post_prevyr<-as.data.frame(role_model_freq_counts_reshape_heatmap_post_prevyr)

 role_model_freq_counts_reshape_heatmap_post_prevyr[is.na(role_model_freq_counts_reshape_heatmap_post_prevyr)] <- 0

role_model_freq_counts_reshape_heatmap_post_prevyr2<-as.matrix(role_model_freq_counts_reshape_heatmap_post_prevyr[, -1])

rownames(role_model_freq_counts_reshape_heatmap_post_prevyr2)<-role_model_freq_counts_reshape_heatmap_post_prevyr$Responses

heatmap(role_model_freq_counts_reshape_heatmap_post_prevyr2)
```
##correlation plot

```{r,fig.width=14, fig.height=12}
role_model_correltion_post_prevyr<-role_model_freq_counts_reshape_heatmap_post_prevyr2[,-1]
#rownames(role_model_correltion_cy)<-colnames(role_model_correltion_cy)
M<-round(cor(role_model_correltion_post_prevyr),1)
ggcorrplot(M,hc.order = TRUE,type='lower',lab=TRUE,lab_size=3, method="circle",colors = c("tomato2", "white", "springgreen3"), ggtheme=theme_bw,title="Correlogram of role models")


```
```{r}

#### sentimental analysis #####

#extracting all the Role Model - Would you like to say who? rows 

Role_Model_who_says_post_prevyr<- role_model_freq_counts_reshape_post_prevyr %>% 
  filter(Questions=="Role Model - Would you like to say who?")

Role_Model_who_says_post_prevyr

```
```{r}

Role_Model_who_says_post_prevyr<-Role_Model_who_says_post_prevyr[2]
role_vec_post_prevyr <- as.matrix(Role_Model_who_says_post_prevyr)
role_vec_post_prevyr_spl_cha_remove<- gsub(".","",role_vec_post_prevyr,fixed=TRUE)
role_vec_post_prevyr_spl_cha_remove<- as.vector(role_vec_post_prevyr_spl_cha_remove)
role_vec_post_prevyr_spl_cha_remove



```


```{r,fig.width=14, fig.height=12}
## extract role answers  columns

##corpus

docs_post_prevyr<- Corpus(VectorSource(role_vec_post_prevyr_spl_cha_remove))

# Convert the text to lower case
docs_post_prevyr <- tm_map(docs_post_prevyr, content_transformer(tolower))
# Remove numbers
docs_post_prevyr <- tm_map(docs_post_prevyr, removeNumbers)
# Remove english common stopwords
docs_post_prevyr <- tm_map(docs_post_prevyr, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
# Remove punctuations
docs_post_prevyr <- tm_map(docs_post_prevyr, removePunctuation)
# Eliminate extra white spaces
docs_post_prevyr <- tm_map(docs_post_prevyr, stripWhitespace)
# Text stemming
docs_post_prevyr <- tm_map(docs_post_prevyr, stemDocument)



dtm_post_prevyr <- TermDocumentMatrix(docs_post_prevyr)
m_post_prevyr <- as.matrix(dtm_post_prevyr)
v_post_prevyr <- sort(rowSums(m_post_prevyr),decreasing=TRUE)
d_post_prevyr <- data.frame(word = names(v_post_prevyr),freq=v_post_prevyr)
rownames(d_post_prevyr)<- NULL ## remove rownames from dataframe
d_post_prevyr<-d_post_prevyr %>% filter(word !="null")

d_post_prevyr
p_post_prevyr<-ggplot(d_post_prevyr,aes(word,freq))+geom_bar(stat="identity")+geom_text(aes(label=freq))
p_post_prevyr<-p+theme(axis.text.x = element_text(angle = 90, hjust = 1))

word_rolemodel_postprev<-wordcloud(words = d_post_prevyr$word,scale=c(7.5,0.5),freq = d_post_prevyr$freq, min.freq = 1,max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))
word_rolemodel_postprev

```


```






